---
title: "MPG analisys"
subtitle: "Report for Motor Trends"
author: "Joaquin Solino Perez"
date: "30-05-2021"
output: pdf_document
---

```{r setup, include=FALSE}
library(datasets)
library(dplyr)
library(ggplot2)
library(GGally)

knitr::opts_chunk$set(echo = TRUE)
```

## Summary 

This document covers the analysis and conclusions about the impact of transmission type (automatic vs manual) in fuel consumption. Specifically, the aim of this document is to answer the next questions:

+ Is an automatic or manual transmission better for fuel consumption?
* Quantify the difference between automatic and manual transmissions, expressed in MPG (miles per galon)


## Car Road Tests

The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973–74 models).

The data is collected in 11 variables in `mtcars` data set. You can see the format of the variables in [Apendix A](# Apendix A). Let's see a summary of the `mtcars`:

```{r cars}
my_cars <- mtcars %>% 
        mutate( mpg = mpg,
                   am = factor(am, labels = c("manual","automatic")),
                   vs = factor(vs, labels = c("V","S")))

summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```


# Apendix A

## Description of `mtcars` dataset

A data frame with 32 observations on 11 (numeric) variables.

[, 1]	mpg	Miles/(US) gallon
[, 2]	cyl	Number of cylinders
[, 3]	disp	Displacement (cu.in.)
[, 4]	hp	Gross horsepower
[, 5]	drat	Rear axle ratio
[, 6]	wt	Weight (1000 lbs)
[, 7]	qsec	1/4 mile time
[, 8]	vs	Engine (0 = V-shaped, 1 = straight)
[, 9]	am	Transmission (0 = automatic, 1 = manual)
[,10]	gear	Number of forward gears
[,11]	carb	Number of carburetors

